%What would you have done dif-
%ferently if you were to do it all over again? How did
%teamwork and communication, both intra- and inter-
%group, turn out?
\section{Self Assessment}
We feel that we have solve the problem satisfactory. There are, however,
some things that could have been done differently. One thing is that the
group could have had more frequent meetings. One group members said that
he felt he had to start from the beginning every time we had a meeting,
because there were such a long time since the last time. Another thing
we could have done better is to involve all the group members in a more
substantial way. 

The communication within the group worked well enough, but could of
course have been even better. The group have communicated using mail,
IRC and during group meetings. There have been a total of two group
meetings during the operation phase, however some of the group members
were not attending one, or both of, the meetings. The second meeting was
planned during the first meeting, so the group member that was not
present at the first meeting was not aware of the second meeting, and
was thus not present there either. This could have been done a lot
better. A mail should have been sent to the entire group with details
about time and place for the meeting.

The group have had only a little communication with other groups,
through IRC, when necessary. This was mostly the webmail group needing
information from us, regarding our setup. This worked very well.
