%What worked? What broke? Did you meet
%the SLA? (We grade you by your reports and pre-
%sentations, not by your technical accomplishments.
%Please be honest.)
\section{Status}
In this section we will evaluate our accomplishments according to the SLA. 

\subsection{Performance}
\begin{itemize}
\item \textbf{70\% of all spam should be filtered or marked on delivery from an
external machine.}

Sending and receiving mail (both local on the system, and through IMAP)
did functioning throughout the operational phase.
We did not have time to install/configure SpamAssassin before the
operational phase, which means the server could receieve more spam than
we agreed to in the SLA.

\item \textbf{90\% of all mails should be delivered to local mailboxes within 10
seconds from delivery.}
\item \textbf{90\% of all outgoing mail should be attempted sent within 10
seconds of sending.}

We cannot guarantee delivery within 10 seconds as according to the SLA. We
initially thought exim automatically logged and generated reports based on
attempted delivery time, but this feature was disabled by default. However, all of our sample tests
showed that email was indeed delivered within the 10 second specification, we
cannot with 100\% certainty guarantee this for all mail. 

\item \textbf{The system should not offer an open mail relay. Any mail attempted
sent shall be authenticated by the system before attempted delivery.}

Exim was set up to disallow any attempted delivery from external users. This was
monitored using eximstats, as shown above. 

\end{itemize}

